Experience Report: Haskell in Computational Biology

### 2012-03-06 mrfy_experience_report.tex
make the code work with plain latex

@@

\begin{figure}\centerline{\includegraphics[width=6cm]{alignment.pdf}} 
\caption{Protein sequences are put into alignment based on structural or 
sequence similarities. Each column of the alignment corresponds to a node of 
the hidden Markov model; columns with many gaps will induce highly probable 
insertion states in the HMM, while columns with fewer gaps will induce 
more-probable deletion and match states. Columns with strong consensus towards 
a particular residue will induce match states with high emission probability 
for that residue.}\label{alignment} \end{figure}

@@

\begin{figure} \centerline{\includegraphics[width=8cm]{Plan7.pdf}} \caption{The 
directed graph representing the states of a traditional HMMER ``Plan7'' hidden 
Markov model. Only 7 of the possible 9 state transitions are allowed, which 
simplifies the dynamic programming. Insertion states represent mutations that 
insert an amino acid, deletion states represent mutations that lose an amino 
acid, and match states represent either conserved amino acids (those with no 
changes) or mutations that substitute one amino acid for another. Each match or 
insertion state has an associated table of emission probabilities (here 
illustrated only for the first two states). Triplets of insertion, deletion, 
and match states are grouped into ``nodes,'' represented here with dashed 
ovals; each node corresponds to a column in the original alignment used to 
train the HMM.}\label{plan7} \end{figure}

@@

\begin{figure}[h!] 
\centerline{\includegraphics[width=8cm]{mrf_interleave_diagram.pdf}} 
\caption{The directed graph representing the states of a MRFy Markov random 
field finite state automaton. Shaded nodes represent beta-strand positions which have been fixed into match states, 
while the dashed edges represent the long-range dependencies due to hydrogen 
bonding. Note that in between the beta-strand regions are normal HMMs.}\label{mrf} \end{figure}

>>>>

\newif\ifpdfmadness

\ifx\pdfoutput\undefined
   \pdfmadnessfalse
\else
   \ifnum\pdfoutput=1
     \pdfmadnesstrue
   \else
     \pdfmadnessfalse
   \fi
\fi

@@

\begin{figure}
\ifpdfmadness
\centerline{\includegraphics[width=6cm]{alignment.pdf}} 
\else
\centerline{\includegraphics[width=6cm]{alignment.eps}} 
\fi

\caption{Protein sequences are put into alignment based on structural or 
sequence similarities. Each column of the alignment corresponds to a node of 
the hidden Markov model; columns with many gaps will induce highly probable 
insertion states in the HMM, while columns with fewer gaps will induce 
more-probable deletion and match states. Columns with strong consensus towards 
a particular residue will induce match states with high emission probability 
for that residue.}\label{alignment} 
\end{figure}

@@

\begin{figure} 
\ifpdfmadness
\centerline{\includegraphics[width=8cm]{Plan7.pdf}} 
\else
\centerline{\includegraphics[width=8cm]{Plan7.eps}} 
\fi

\caption{The 
directed graph representing the states of a traditional HMMER ``Plan7'' hidden 
Markov model. Only 7 of the possible 9 state transitions are allowed, which 
simplifies the dynamic programming. Insertion states represent mutations that 
insert an amino acid, deletion states represent mutations that lose an amino 
acid, and match states represent either conserved amino acids (those with no 
changes) or mutations that substitute one amino acid for another. Each match or 
insertion state has an associated table of emission probabilities (here 
illustrated only for the first two states). Triplets of insertion, deletion, 
and match states are grouped into ``nodes,'' represented here with dashed 
ovals; each node corresponds to a column in the original alignment used to 
train the HMM.}\label{plan7} \end{figure}

@@

\begin{figure}[h!] 
\ifpdfmadness
\centerline{\includegraphics[width=8cm]{mrf_interleave_diagram.pdf}} 
\else
\centerline{\includegraphics[width=8cm]{mrf_interleave_diagram.eps}} 
\fi
\caption{The directed graph representing the states of a MRFy Markov random 
field finite state automaton. Shaded nodes represent beta-strand positions which have been fixed into match states, 
while the dashed edges represent the long-range dependencies due to hydrogen 
bonding. Note that in between the beta-strand regions are normal HMMs.}\label{mrf} \end{figure}
